Estimating Animal Abundance with N-Mixture Models Using the \pkg{R-INLA} Package for R

### 2017-04-25 meehan_et_al_inla_nmix_jss/article.tex
Small manuscript fix

The call to the inla() function includes several components. First is the model statement. On the left side of the formula is the counts.and.count.covs object that includes the matrix of counts and the covariates related to $\lambda$.  On the right side of the formula is a 1 to specify a global intercept for $p$ and the two covariates for $p$.  Note that a wide range of random effects for $p$ could be added to the right side of the formula using the f() syntax \citep{Rue_Martino_Lindgren_Simpson_Riebler_2013}. The second argument describes the data, provided here as a list that corresponds with the model formula. Third is the likelihood family, which can take values of "nmix" for a Poisson-Binomial mixture and "nmixnb" for a Negative Binomial-Binomial mixture. The fourth (control.fixed, for detection parameters) and fifth (control.family, for abundance and overdispersion parameters) arguments specify the priors for the two model components. In this case, the priors are specified similarly to those in the \proglang{JAGS} model, but a variety of other options are available. Several other characteristics of the analysis can be modified in the call to inla(). See \cite{Rue_Martino_Lindgren_Simpson_Riebler_2013} for details.

@@

%% discussion
\section[Discussion]{Discussion}
The purpose of this study was to demonstrate the use of the \pkg{R-INLA} package \citep{Rue_Martino_Lindgren_Simpson_Riebler_2013} to analyze N-mixture models and to compare performance of \pkg{R-INLA} to two other common approaches, \proglang{JAGS} \citep{plummer2003jags,Lunn_Jackson_Best_Thomas_Spiegelhalter_2012}, via the \pkg{runjags} package \citep{Denwood_2016}, which employs MCMC methods and allows Bayesian inference, and the \pkg{unmarked} package \citep{Fiske_Chandler_others_2011}, which uses Maximum Likelihood and allows frequentist inference.

>>>>

The call to the inla() function includes several components. First is the model statement. On the left side of the formula is the counts.and.count.covs object that includes the matrix of counts and the covariates related to $\lambda$.  On the right side of the formula is a 1 to specify a global intercept for $p$ and the two covariates for $p$.  Note that a wide range of random effects for $p$ could be added to the right side of the formula using the f() syntax \citep{Rue_Riebler_Sorbye_Illian_Simpson_Lindgren_2017}. The second argument describes the data, provided here as a list that corresponds with the model formula. Third is the likelihood family, which can take values of "nmix" for a Poisson-Binomial mixture and "nmixnb" for a Negative Binomial-Binomial mixture. The fourth (control.fixed, for detection parameters) and fifth (control.family, for abundance and overdispersion parameters) arguments specify the priors for the two model components. In this case, the priors are specified similarly to those in the \proglang{JAGS} model, but a variety of other options are available. Several other characteristics of the analysis can be modified in the call to inla(). See \cite{Rue_Riebler_Sorbye_Illian_Simpson_Lindgren_2017} for details.

@@

%% discussion
\section[Discussion]{Discussion}
The purpose of this study was to demonstrate the use of the \pkg{R-INLA} package \citep{Rue_Riebler_Sorbye_Illian_Simpson_Lindgren_2017} to analyze N-mixture models and to compare performance of \pkg{R-INLA} to two other common approaches, \proglang{JAGS} \citep{plummer2003jags,Lunn_Jackson_Best_Thomas_Spiegelhalter_2012}, via the \pkg{runjags} package \citep{Denwood_2016}, which employs MCMC methods and allows Bayesian inference, and the \pkg{unmarked} package \citep{Fiske_Chandler_others_2011}, which uses Maximum Likelihood and allows frequentist inference.
